---
title: "Well-being by Demographics"
---

> The projects should be numbered consecutively (i.e., in the order in which you began them), and should include for each project a description of the goal, the product (computer program, hand graph, computer graph, etc.), the data, and some interpretation. Reports must be reproducible and of high quality in terms of writing, grammar, presentation, etc.

```{r load-packages, warning = FALSE, message=FALSE}
library(tidyverse) 
library(tidyr)
library(haven)
library(forcats)

confession <- read_sav("C:/Users/krysc/OneDrive/Desktop/Catholicism Study/with recode and UPDATED WHO WELLBEING SCORE scores.sav")
View(confession)
```

MAIN QUESTION: HOW OFTEN DO DIFFERENT GROUPS ATTEND CONFESSION?!

For this project, I will be examining the relationship between confession attendance and different demographics variables such as political orientation, yearly income, gender, education, and age. To begin, I have read in my data from SPSS using the code from the "Import Dataset" tab. 

For this project, I will run bar plots showing the confession attendance of different demographic variables. To begin, I will examine the frequency of confession attendance for different political orientations

```{r}

select(
  confession, 
  RECODEConfAttend,
  Q106
)

confession <- confession %>%
  mutate(
    Q106 = as.character(Q106),
    Poli_Orientation = case_when(
      Q106 == "1" ~ "Democrat",
      Q106 == "2" ~ "Republican", 
      Q106 == "3" ~ "Independent",
      Q106 %in% c("4", "5", "6", "NA") ~ "Other",
      TRUE ~ NA_character_
    )
  )


ggplot(data = confession, aes(x = RECODEConfAttend)) +
  geom_bar()+
  facet_wrap(~Poli_Orientation, nrow = 2) +
  labs(title = "Political Orientation and Confession Attendance",
       x = "Confession Attendance")
  
```


Sed mollis purus faucibus leo finibus, ut pharetra nibh elementum. Nulla id orci lorem. Mauris sollicitudin mi eget tellus vehicula, ut convallis lorem mollis. In blandit nulla diam, a malesuada sem volutpat interdum. Ut elementum elit at velit maximus, ac tempor odio porttitor. Suspendisse lobortis sollicitudin tortor, ut pharetra libero luctus a. Sed hendrerit faucibus metus. Sed rutrum purus vel pellentesque euismod.


```{r}
# Create a barplot of the number of fish encounters by species
ggplot(data = confession, aes(x = WHO_WELLBEING_Score)) +
  geom_bar()+
  facet_wrap(~Poli_Orientation, nrow = 2) +
  labs(title = "Political Orientation and Confession Attendance",
       x = "Confession Attendance")
```

Mauris placerat in velit a pharetra. Nulla viverra bibendum lectus, ut lobortis nibh. Aenean malesuada, orci vitae dictum placerat, enim justo aliquet leo, ac tincidunt augue ipsum et mi. Nullam in pharetra metus, nec molestie felis. Duis varius rhoncus pulvinar. Integer semper urna sed tellus rhoncus, vel suscipit odio iaculis. Mauris iaculis neque pellentesque ex convallis venenatis. Sed ultrices euismod fermentum. Ut feugiat risus at turpis tincidunt viverra.



```{r}

ggplot(data = confession, aes(x = RECODEConfAttend, y = Divine_Forgiveness_Mean)) +
  geom_point(aes(colour = factor(Poli_Orientation)), size = .5)

```



```{r}
# Create a barplot of the number of fish encounters by species
ggplot(data = confession, aes(x = EXAMCONSCI_TOTAL, y = Divine_Forgiveness_Mean)) +
  geom_point()
  
```

Donec sagittis suscipit orci in ultrices. Vivamus iaculis eleifend est et dictum. Fusce non urna at lacus dapibus tincidunt ac sed nibh. Donec luctus lectus elit, ac ultrices tortor mollis sit amet. Nulla finibus lacinia arcu. Proin sollicitudin non odio et pulvinar. Maecenas finibus faucibus finibus. Ut elementum metus velit, a sodales sapien commodo et. Vivamus pulvinar, sapien et porta cursus, elit est luctus nisi, eget fringilla odio diam et enim. Sed sodales suscipit bibendum. Morbi ut metus semper, laoreet felis sodales, consequat dolor.
