---
title: "Portfolio 6"
---

For this portfolio piece, I wanted to test myself and see if I could run some of the analyses I ran for my FYP in SPSS in R. While I did not re-run all of my analyses, I did run a subset of them. The dataset used is also already mainly cleaned. I primarily wanted to practice recoding and mean scoring and then running correlations. 

```{r}
library(tidyverse) 
library(tidyr)
library(haven)
library(forcats)
library(ggplot2)

confession <- read_sav("C:/Users/krysc/OneDrive/Desktop/Catholicism Study/with recode and UPDATED WHO WELLBEING SCORE scores.sav")
```

```{r}

library(tidyverse)

confessionClean <- confession %>%
  #Attention Check Filter
  filter(Attention_Check3 == 5)

confessionClean <- confession %>%
  mutate(
    # Recode measures that are on a scale of 1 to 5 (Trait Self Control & Moral Tolerance)
    across(c(Trait_Self_Control_2, Trait_Self_Control_3, Trait_Self_Control_4, 
             Trait_Self_Control_5, Trait_Self_Control_7, Trait_Self_Control_9, 
             Trait_Self_Control_10, Trait_Self_Control_12, Trait_Self_Control_13,
             Moral_Tolerance_3, Moral_Tolerance_5, Moral_Tolerance_7), 
           ~ 6 - .x, .names = "{.col}R"),
    
  )

confessionClean <- confession %>%
  rowwise() %>% 
  mutate(
    TraitSelfControl_Mean = mean(c(Trait_Self_Control_1, TRAITSC_2R, TRAITSC_3R, 
                                   TRAITSC_4R, TRAITSC_5R, Trait_Self_Control_6, 
                                   TRAITSC_7R, Trait_Self_Control_8, TRAITSC_9R, 
                                   TRAITSC_10R, Trait_Self_Control_11, TRAITSC_12R, 
                                   TRAITSC_13R), na.rm = TRUE),
    
    Depression_Mean = mean(c(Distress_1, Distress_2, Distress_3, Distress_4, Distress_5, Distress_6, Distress_7), na.rm = TRUE),
    
    WHO_WELLBEING_Score = sum(c(WHO_Well_Being_Index_1, WHO_Well_Being_Index_2, WHO_Well_Being_Index_3, 
                                 WHO_Well_Being_Index_4, WHO_Well_Being_Index_5), na.rm = TRUE) * 4
  ) %>%
  ungroup()

#Correlations
cor_vars <- confessionClean %>% 
  select(SWL_Mean, Flourishing_Mean, WHO_WELLBEING_Score, DepressionPSYCDistress_Mean)

cor(cor_vars, use = "pairwise.complete.obs")

print(cor_vars)

```

```{r}

ggplot(data = confession, aes(x = SWL_Mean, y = WHO_WELLBEING_Score)) +
  geom_point(size = .5) +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(
    title = "Satisfaction with Life and Well-Being",
    x = "SWL",
    y = "Well-Being")

```

```{r}

ggplot(data = confession, aes(x = SWL_Mean, y = Flourishing_Mean)) +
  geom_point(size = .5) +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(
    title = "Satisfaction with Life and Flourishing",
    x = "SWL",
    y = "Flourishing")


```

```{r}

ggplot(data = confession, aes(x = SWL_Mean, y = DepressionPSYCDistress_Mean)) +
  geom_point(size = .5) +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(
    title = "Satisfaction with Life and Depression",
    x = "SWL",
    y = "Depression")

```

The plots above are meant to model the correlations between SWL and Depression, Well-Being, and Flourishing. Consistent with the correlation matrix, there is a positive relationship between satisfaction with life and well-being and flourishing and a negative relationship between SWL and depression. 