---
title: "Project Sekai Data"
---

For this project, I got some data from the Wiki from one of my favorite mobile games. I tried webscraping but that simply did not work. 

For this piece, I would love to calculate how many cards exist for each character, the most frequent rarity and availability (limited or not) for each character, and also generate a graph of popularity for each character. The variables are below: 

+ Name: Name of the card 
+ Unit/Group: Name of the group
  + Vivid Bad Squad
    + Azusawa Kohane
    + Shiraishi An  
    + Shinonome Akito  
    + Aoyagi Toya
  + Nightcord at 25:00 
    + Yoisaki Kanade  
    + Asahina Mafuyu  
    + Shinonome Ena  
    +Akiyama Mizuki
  + More More Jump! 
    + Hanasato Minori  
    + Kiritani Haruka  
    + Momoi Airi  
    + Hinomori Shizuku
  + Leo Need
    + Hoshino Ichika
    + Tenma Saki
    + Mochizuki Honami
    +Hinomori Shiho
  + Wonderlands x Showtime 
    + Tenma Tsukasa  
    + Otori Emu  
    + Kusanagi Nene  
    + Kamishiro Rui
  + Virtual Singer
    + Hatsune Miku
    + Kagamine Rin
    + Kagamine Len
    + Megurine Luka
    + MEIKO
    + KAITO
+ Character: Name of the character 
  + Character names are listed above under their respective groups.
+ Type: The attribute assigned to each card. 
  + Mysterious 
  + Cool
  + Pure 
  + Happy
  + Cute
+ Rarity: The level of rarity for each card. On a scale of 1 to 4. Birthday rarity is similar to 4 star rarity but is exclusive to characters birthdays 
+ Availability: Determines when you get the card and how long it sticks around 
  + Limited: Only present for a short amount of time. Will appear one more time and then is gone forever. Leads to much heartbreak. 
  + Permanent: You could get this card at any time and it will never go away. Usually the cards related to a permanent event. 
  + BD/AN Limited: Similar to Limited but exclusive for birthdays and anniversaries (virtual singers only have anniversaries, not birthdays)
+ Skill Type: Determines what buffs it gives during gameplay. 
  + Scorers 
  + Lockers 
  + Healers
  + Hybrid
  + High-Tier Competitive Skills
+ Released: When the card first came out 
+ Event: The event related to the card. N/A for limited cards
+ Costume: Some cards get special costumes to go along with them. This will coded as present or not. 
  
## Data Cleaning 

To begin, I loaded in the data and the packages. Then, I changed the symbols for the rarity variable into numbers. Then I made a new variable that accounts for whether the card had a costume and was associated with an event or not. This will make charting my graphs much easier. While graphing I ran into an issue with the 'group' variable and changed it to unit to make R less angry. 

```{r}

library(tidyverse)
library(readxl)

pjsk_csv <- read_excel("pjsk.csv.xlsx")

library(tidyverse)

df_cleaned <- pjsk_csv %>%
  mutate(
    rarity_numeric = case_when(
      str_detect(Rarity, "🎀") ~ 4,
      TRUE ~ as.numeric(str_count(Rarity, "⭐"))
    ),
      has_costume = case_when(
      is.na(Costume) | Costume == "" | Costume == "None" | Costume == "-" ~ "Not Present",
      TRUE ~ "Present"
    ),
    
    is_event_card = case_when(
      is.na(Event) | Event == "" | Event == "None" | Event == "-" ~ "No",
      TRUE ~ "Yes"
    )
  )

library(tidyverse)

colnames(df_cleaned) <- tolower(trimws(colnames(df_cleaned)))

print(colnames(df_cleaned))

df_cleaned <- df_cleaned %>% 
  rename(unit = "group")

```

## Data Analysis 

Next, I wanted to see how many cards existed for each group. As such, I generated a bar graph and factored that by groups. I do the same thing for characters, as well. 

```{r}

ggplot(df_cleaned, aes(x = fct_infreq(unit), fill = unit)) +
  geom_bar() +
  labs(
    title = "Distribution of Cards by Group",
    x = "Unit / Group",
    y = "Number of Cards"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

```

```{r, figh.width = 20, fig.height=20 }
ggplot(df_cleaned, aes(x = fct_infreq(character))) +
  geom_bar() +
  labs(
    title = "Total Cards per Character",
    x = "Character Name",
    y = "Number of Cards"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    legend.position = "bottom"
  )

```